\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-19 paper/main.tex
minor cleanup and grammatical fixes throughout

The same computer code may not behave identically under different
circumstances.  For example, when code depends on external libraries,
different versions of those libraries may function differently.  Or
when CPU or GPU instruction sets differ across machines, the same
high-level code may be compiled into different machine instructions.
Because executing identical code does not guarantee identical
outcomes, code sharing in and of itself is often insufficient for
enabling researchers to reproduce each others' work.

Within the Python~\citep{vanR95} community, external
packages that are published in the most popular
repositories~\citep{pypi, cond15} are associated with version numbers
and tags that enable users to guarantee that they are installing
exactly the same code across different computing environments.
Despite that it is \textit{possible} to manually install the intended
version numbers of every dependency of a Python script or package, manually
tracking down those dependencies can impose a substantial burden on
the user.

@@

Researchers, programmers, and others have developed a broad
set of approaches and tools to facilitate code sharing and
reproducible outcomes (Fig.~\ref{fig:code-sharing}).  At one
extreme, simply publishing a set of Python scripts (.py files) may
enable others to use or gain insights into the relevant work.  Because
Python is installed by default on most modern operating systems, for
some projects this may be sufficient.  Another popular approach
entails creating JSON files, called Jupyter
notebooks~\citep{KluyEtal16}, that comprise a mix of text, executable
code, and embedded media.  Notebooks may call or import external
scripts or libraries in order to provide a more compact and readable
experience for users.  Each of these systems (Python scripts and
notebooks) provides a convenient means of sharing code, with the
caveat that they do not specify the computing environment in which the
code is executed.  Therefore the functionality of code shared using
these systems cannot be guaranteed across different computing
environments.

At another extreme, virtual machines~\citep{Gold74, AltiEtal05,
  Rose99} provide a hardware-level simulation of the desired system.
Virtual machines are typically isolated from the user's system, such
that installing or running software on a virtual machine does not
impact the user's primary operating system or computing environment.
Containers~\citep[e.g.,][]{Merk14, KurtEtal17} provide a similar
``isolated'' experience.  Although containerized environments do not
specify hardware-level operations, they are typically packaged with a
complete operating system, in addition to a complete copy of Python
and any relevant package dependencies.  Virtual
environments~\citep[e.g.,][]{Anac12} also provide a computing
environment that is largely separated from the user's main
environment.  They incorporate a copy of Python and the target
software's dependencies, but virtual environments do not specify or
reproduce an operating system for the runtime environment.  Each of
these systems (virtual machines, containers, and virtual environments)
guarantees (to differing degrees-- at the hardware level, operating
system level, and Python environment level, respectively) that the
relevant code will run similarly for different users.  However, each
of these systems also relies on additional software that can be
resource intensive or burdensome to install or configure.

We designed \texttt{davos} to occupy a ``sweet spot'' between these
extremes.  \texttt{davos} is a notebook-installable package that adds
functionality to the default notebook experience.  Like standard
Jupyter notebooks, \texttt{davos}-enhanced notebooks allows
researchers to include text, executable code, and media within a
single file.  No further setup or installation is required, beyond
what is needed to run standard Jupyter notebooks.  And like virtual
environments \texttt{davos} provides a convenient mechanism for fully
specifying (and installing, as needed) a complete set of Python
dependencies, including package versions.

@@

\subsection{Software architecture}
% Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
The \texttt{davos} package consists of two interdependent subpackages (see Fig.~\ref{fig:package-structure}). The first, \texttt{davos.core}, comprises a set of modules that implement\comment{provide?} the bulk of the package's core functionality, including pipelines for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section \ref{subsec:smuggle}) and onion comment (see Section \ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section \ref{subsec:config}). However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementation approaches depending on various properties of the notebook environment in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython \cite{PereGran07} is used by the notebook kernel). To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions'' in the \texttt{davos.implementations} subpackage. This second subpackage defines multiple, interchangeable versions of each helper function, organized into\comment{per-environment} modules by the conditions that trigger their use. At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment in a single, consistent location. An additional benefit of this design pattern is that it allows maintainers or users to easily extend \texttt{davos} to support new, updated, or custom notebook variants simply by creating a new \texttt{davos.implementations} module with any necessary tweaks to existing helper functions.

@@

\subsection{Software functionalities}
% Present the major functionalities of the software.
\subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
Importing \texttt{davos} in an IPython notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section \ref{subsec:implementation} for details on how this works).
The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
However, whereas \texttt{import} will fail if the requested package is not installed locally, \texttt{smuggle} statements can handle missing packages on the fly.
If a smuggled package does not exist in the local environment, \texttt{davos} will install it automatically, expose its contents to Python's \texttt{import} machinery, and load it into the namespace for immediate use.

\subsubsection{The onion comment}\label{subsec:onion}
For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment''. An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it. Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar. To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line:
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet1.pdf}
\end{center}
Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it):
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet2.pdf}
\end{center}
However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}. If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will ensure that the version of the package loaded into the notebook always matches the specific version requested, or satisfies the given version constraints. If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided. If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead:
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet3.pdf}
\end{center}
Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.):
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet4.pdf}
\end{center}
\texttt{davos} processes onion comments internally before forwarding arguments to the installer program. In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed. For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section \ref{subsec:onion}); and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported:
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet5.pdf}
\end{center}

\subsubsection{The \texttt{davos} config}\label{subsec:config}
The \texttt{davos} config object provides a simple, high-level interface that allows users to view and set various options that affect \texttt{davos}'s behavior. After importing \texttt{davos}, the config instance (a singleton) for the current session is available as \texttt{davos.config}, and its various fields are accessible as attributes. The config object exposes a mixture of writable and read-only fields. Writable fields include:
\begin{itemize}
\item \texttt{.active}: Whether or not \texttt{davos} functionality (i.e., support for \texttt{smuggle} statements and onion comments) should be enabled for subsequent code. Defaults to \texttt{True} when \texttt{davos} is first imported. See Section \ref{subsec:implementation} for additional info.
\item \texttt{.auto\_rerun}: Controls behavior if \texttt{davos} is used to \texttt{smuggle} a new version of a package that was previously imported and cannot be reloaded (i.e., it contains C-extensions that dynamically generate code). If \texttt{True} (default: \texttt{False}), \texttt{davos} will automatically restart the notebook kernel and rerun all code up to (and including) the current \texttt{smuggle} statement. Otherwise, \texttt{davos} will issue a warning, pause execution, and prompt the user with buttons to either restart \& rerun the notebook or continue running with the imported package version. (Note: not configurable in Google Colaboratory).
\item \texttt{.confirm\_install}: If \texttt{True} (default: \texttt{False}), \texttt{davos} will require user confirmation (\texttt{[y]es/[n]o} input) before installing a smuggled package.
\item \texttt{.noninteractive}: Setting to \texttt{True} (default: \texttt{False}) enables non-interactive mode, in which all user input and confirmation is disabled. Note that in non-interactive mode, the \texttt{confirm\_install} option is set to \texttt{False}, and if \texttt{auto\_rerun} is \texttt{False}, \texttt{davos} will throw an error if a smuggled package cannot be reloaded.
\item \texttt{.pip\_executable}: The path to the \texttt{pip} executable used to install smuggled packages. Default is programmatically determined from the Python environment and falls back to \texttt{sys.executable -m pip} if one can't be found.
\item \texttt{.suppress\_stdout}: If \texttt{True} (default: \texttt{False}), suppress all unnecessary output issued by both \texttt{davos} and the installer program. Useful when smuggling packages that need to install many dependencies and/or generate extensive output. If the installer program throws an error, both stdout and stderr will be shown with the traceback.
\end{itemize}

@@

The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above). When \texttt{davos} is first imported, it is activated automatically. Activating \texttt{davos} triggers two actions: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer. IPython preprocesses all executed code as plain text before it is sent to the Python parser, in order to handle special constructs like \texttt{\%magic} and \texttt{!shell} commands. \texttt{davos} hooks into this process to transform \texttt{smuggle} statements into syntactically valid Python code. The \texttt{davos} parser uses a complex regular expression \cite{Thom68} to match lines of code containing \texttt{smuggle} statements (and, optionally, onion comments), extract relevant information from their text, and replace them with equivalent calls to the \texttt{smuggle()} function. For example, if a user runs a notebook cell containing
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet6.pdf}
\end{center}
the code that is actually executed by the Python interpreter would be
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet7.pdf}
\end{center}
Because the \texttt{smuggle()} function is defined in the notebook namespace, it is also possible (though never necessary) to call it directly. Deactivating \texttt{davos} will delete the name ``\texttt{smuggle}'' from the namespace, unless its value has been overwritten and no longer refers to the \texttt{smuggle()} function. It will also deregister the \texttt{davos} parser from the set of input transformers run when each notebook cell is executed. While the overhead added by the \texttt{davos} parser is de minimis, this may be useful, for example, when optimizing or precisely profiling code.

@@

Since its initial release, \texttt{davos} has found use in a variety
of applications.  In addition to managing computing environments
for multiple ongoing research studies, \texttt{davos} is being used by
both students and instructors in programming courses such as
\href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling
    with Data}} \cite{Mann21b} (an open course on data science,
visualization, and communication) to simplify distributing lessons and
submitting assignments, as well as in online demos such as
{\texttt{abstract2paper}} \cite{Mann21a} (an example application of
\href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share
ready-to-run code that installs dependencies automatically.

>>>>

The same computer code may not behave identically under different
circumstances.  For example, when code depends on external libraries,
different versions of those libraries may function differently.  Or
when CPU or GPU instruction sets differ across machines, the same
high-level code may be compiled into different machine instructions.
Because executing identical code does not guarantee identical
outcomes, code sharing in and of itself is often insufficient for
enabling researchers to reproduce each other's work.

Within the Python~\cite{vanR95} community, external
packages that are published in the most popular
repositories~\cite{pypi, cond15} are associated with version numbers
and tags that enable users to guarantee that they are installing
exactly the same code across different computing environments.
Despite that it is \textit{possible} to manually install the intended
version numbers of every dependency of a Python script or package, manually
tracking down those dependencies can impose a substantial burden on
the user.

@@

Researchers, programmers, and others have developed a broad
set of approaches and tools to facilitate code sharing and
reproducible outcomes (Fig.~\ref{fig:code-sharing}). At one
extreme, simply publishing a set of Python scripts (\texttt{.py} files) may
enable others to use or gain insights into the relevant work. Because
Python is installed by default on most modern operating systems, for
some projects this may be sufficient. Another popular approach
entails creating JSON files called Jupyter
notebooks~\cite{KluyEtal16} that comprise a mix of text, executable
code, and embedded media. Notebooks may call or import external
scripts or libraries in order to provide a more compact and readable
experience for users. Each of these systems (Python scripts and
notebooks) provides a convenient means of sharing code, with the
caveat that they do not specify the computing environment in which the
code is executed. Therefore the functionality of code shared using
these systems cannot be guaranteed across different computing
environments.

At another extreme, virtual machines~\cite{Gold74, AltiEtal05,
 Rose99} provide a hardware-level simulation of the desired system.
Virtual machines are typically isolated from the user's system, such
that installing or running software on a virtual machine does not
impact the user's primary operating system or computing environment.
Containers~\cite[e.g.,][]{Merk14, KurtEtal17} provide a similar
``isolated'' experience. Although containerized environments do not
specify hardware-level operations, they are typically packaged with a
complete operating system, in addition to a complete copy of Python
and any relevant package dependencies. Virtual
environments~\cite[e.g.,][]{Anac12} also provide a computing
environment that is largely separated from the user's main
environment. They incorporate a copy of Python and the target
software's dependencies, but virtual environments do not specify or
reproduce an operating system for the runtime environment. Each of
these systems (virtual machines, containers, and virtual environments)
guarantees (to differing degrees---at the hardware level, operating
system level, and Python environment level, respectively) that the
relevant code will run similarly for different users. However, each
of these systems also relies on additional software that can be
resource intensive or burdensome to install or configure.

We designed \texttt{davos} to occupy a ``sweet spot'' between these
extremes.  \texttt{davos} is a notebook-installable package that adds
functionality to the default notebook experience. Like standard
Jupyter notebooks, \texttt{davos}-enhanced notebooks allows
researchers to include text, executable code, and media within a
single file. No further setup or installation is required, beyond
what is needed to run standard Jupyter notebooks. And like virtual
environments, \texttt{davos} provides a convenient mechanism for fully
specifying (and installing, as needed) a complete set of Python
dependencies, including package versions.

@@

\subsection{Software architecture}
% Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
The \texttt{davos} package consists of two interdependent subpackages (see Fig.~\ref{fig:package-structure}). The first, \texttt{davos.core}, comprises a set of modules that implement\comment{provide?} the bulk of the package's core functionality, including pipelines for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section~\ref{subsec:smuggle}) and onion comment (see Section~\ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section~\ref{subsec:config}). However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementation approaches depending on various properties of the notebook environment in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython~\cite{PereGran07} is used by the notebook kernel). To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions'' in the \texttt{davos.implementations} subpackage. This second subpackage defines multiple, interchangeable versions of each helper function, organized into modules by the conditions that trigger their use. At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment in a single, consistent location. An additional benefit of this design pattern is that it allows maintainers or users to easily extend \texttt{davos} to support new, updated, or custom notebook variants simply by creating a new \texttt{davos.implementations} module with any necessary tweaks to existing helper functions.

@@

\subsection{Software functionalities}
% Present the major functionalities of the software.
\subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
Importing \texttt{davos} in an IPython notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section~\ref{subsec:implementation} for details on how this works).
The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
However, whereas \texttt{import} will fail if the requested package is not installed locally, \texttt{smuggle} statements can handle missing packages on the fly.
If a smuggled package does not exist in the local environment, \texttt{davos} will install it automatically, expose its contents to Python's \texttt{import} machinery, and load it into the namespace for immediate use.

\subsubsection{The onion comment}\label{subsec:onion}
For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment''. An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it. Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484~\cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar. To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line:
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet1}
\end{center}
Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it):
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet2}
\end{center}
However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}. If an onion comment includes a version specifier~\cite{CoghStuf13}, \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints. If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided. If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead:
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet3}
\end{center}
Onion comments can similarly be used to smuggle specific VCS references (e.g., Git~\cite{TorvHama05}  branches, commits, tags, etc.):
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet4}
\end{center}
\texttt{davos} processes onion comments internally before forwarding arguments to the installer program. In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed. For example, the \texttt{-I}/\texttt{--ignore-installed}, \texttt{-U}/\texttt{--upgrade}, and \texttt{--force-reinstall} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy:
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet5}
\end{center}
Similarly, passing \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section~\ref{subsec:onion}), and installing a smuggled package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported

\subsubsection{The \texttt{davos} config}\label{subsec:config}
The \texttt{davos} config object provides a simple, high-level interface that allows users to view and set various options that affect \texttt{davos}'s behavior. After importing \texttt{davos}, the config instance (a singleton) for the current session is available as \texttt{davos.config}, and its various fields are accessible as attributes. The config object exposes a mixture of writable and read-only fields. Writable fields include:
\begin{itemize}
\item \texttt{.active}: Whether or not \texttt{davos} functionality (i.e., support for \texttt{smuggle} statements and onion comments) should be enabled for subsequent code. Defaults to \texttt{True} when \texttt{davos} is first imported. See Section~\ref{subsec:implementation} for additional info.
\item \texttt{.auto\_rerun}: Controls behavior if \texttt{davos} is used to \texttt{smuggle} a new version of a package that was previously imported and cannot be reloaded (i.e., it contains C-extensions that dynamically generate code). If \texttt{True} (default: \texttt{False}), \texttt{davos} will automatically restart the notebook kernel and rerun all code up to (and including) the current \texttt{smuggle} statement. Otherwise, \texttt{davos} will issue a warning, pause execution, and prompt the user with buttons to either restart \& rerun the notebook or continue running with the imported package version. (Note: not configurable in Google Colaboratory).
\item \texttt{.confirm\_install}: If \texttt{True} (default: \texttt{False}), \texttt{davos} will require user confirmation (\texttt{[y]es/[n]o} input) before installing a smuggled package.
\item \texttt{.noninteractive}: Setting to \texttt{True} (default: \texttt{False}) enables non-interactive mode, in which all user input and confirmation is disabled. Note that in non-interactive mode, the \texttt{confirm\_install} option is set to \texttt{False}, and if \texttt{auto\_rerun} is \texttt{False}, \texttt{davos} will throw an error if a smuggled package cannot be reloaded.
\item \texttt{.pip\_executable}: The path to the \texttt{pip} executable used to install smuggled packages. Default is programmatically determined from the Python environment and falls back to \texttt{sys.executable -m pip} if one can't be found.
\item \texttt{.suppress\_stdout}: If \texttt{True} (default: \texttt{False}), suppress all unnecessary output issued by both \texttt{davos} and the installer program. Useful when smuggling packages that need to install many dependencies and/or generate extensive output. If the installer program throws an error, both stdout and stderr will be shown with the traceback.
\end{itemize}

@@

The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section~\ref{subsec:config}, above). When \texttt{davos} is first imported, it is activated automatically. Activating \texttt{davos} triggers two actions: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer. IPython preprocesses all executed code as plain text before it is sent to the Python parser, in order to handle special constructs like \texttt{\%magic} and \texttt{!shell} commands. \texttt{davos} hooks into this process to transform \texttt{smuggle} statements into syntactically valid Python code. The \texttt{davos} parser uses a complex regular expression~\cite{Thom68} to match lines of code containing \texttt{smuggle} statements (and, optionally, onion comments), extract relevant information from their text, and replace them with equivalent calls to the \texttt{smuggle()} function. For example, if a user runs a notebook cell containing
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet6}
\end{center}
the code that is actually executed by the Python interpreter would be
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet7}
\end{center}
Because the \texttt{smuggle()} function is defined in the notebook namespace, it is also possible (though never necessary) to call it directly. Deactivating \texttt{davos} will delete the name ``\texttt{smuggle}'' from the namespace, unless its value has been overwritten and no longer refers to the \texttt{smuggle()} function. It will also deregister the \texttt{davos} parser from the set of input transformers run when each notebook cell is executed. While the overhead added by the \texttt{davos} parser is de minimis, this may be useful, for example, when optimizing or precisely profiling code.

@@

Since its initial release, \texttt{davos} has found use in a variety
of applications. In addition to managing computing environments
for multiple ongoing research studies, \texttt{davos} is being used by
both students and instructors in programming courses such as
\href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling
    with Data}}~\cite{Mann21b} (an open course on data science,
visualization, and communication) to simplify distributing lessons and
submitting assignments, as well as in online demos such as
{\texttt{abstract2paper}}~\cite{Mann21a} (an example application of
\href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share
ready-to-run code that installs dependencies automatically.
